A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-21 src/paper.tex
Table with URI resources

\usepackage{cite}
\usepackage{graphicx}

@@

>>>>

\usepackage{cite}
\usepackage{graphicx}
\usepackage{array}

@@

\begin{table}[!t]
	\label{tab_web_services_design}
	\renewcommand{\arraystretch}{1.3}
	\caption{Description of the strategies to handle CRUD by mapping HTTP methods onto URIs.}
	\centering
	\begin{tabular}{|l|c|p{3.5cm}|}
		\hline
		\bfseries Resource & \bfseries HTTP Method & \bfseries
		\tabularnewline\hline
		/resource & GET& Retrieves a list of the specified resource 
		\tabularnewline\hline
		/resource/\emph{\{id\}} & GET & Retrieves a specific resource identified by \emph{\{id\}}
		\tabularnewline\hline
		/resource & POST & Creates a new resource 
		\tabularnewline
		\hline
		/resource/\emph{\{id\}} & PUT & Updates a resource identified by \{id\}
		\tabularnewline
		\hline
		/resource/\emph{\{id\}} & DELETE & Deletes a resource identified by \emph{\{id\}}
		\tabularnewline
		\hline
	\end{tabular}
\end{table}
